---
title: "Paper title"
author: "Your Name"
email: your.email@some.edu
department: Your department
address: Your address
date: "12/05/2017"
output:
  pdf_document:
    template: ccn_style.tex
    fig_caption: true

header-includes:
  - \usepackage{hyperref}

abstract: 
  "The abstract should be identical to the text version submitted in the webform and should not exceed 1,500 characters, including spaces and any special characters. The abstract should thus be relatively short. Aim for 150 words. Max length is 200 words. Arbitrarily long German words are not encouraged. CCN has an interdisciplinary audience. Hence a good abstract should (a) give context about what the problem is and why it matters (b) give the contents and explain what was done and what was found (c) give a clear conclusion including what we learned and how it changes the way we think about the universe."

keywords: put; your; keywords; here
bibliography: ./ccn_style.bib
---

```{r setup, include=FALSE}
library(ggplot2)

```

# General Formatting Instructions

The entire contribution of a short summary submission (including
figures, references, and anything else) can be no longer than two
pages. This short summary format is to be used for workshop and
tutorial descriptions, symposia summaries, and publication-based
presentation extended abstracts. Unlike submitted research papers,
short summary submissions should _not_ begin with a separate
abstract. Prior to the first section of the short summary, there
should be the header __Keywords:__ followed by a list of
descriptive keywords separated by semicolons, all in 9~point font, as
shown above.

The text of the paper should be formatted in two columns with an
overall width of 7 inches (17.8 cm) and length of 9.25 inches (23.5
cm), with 0.25 inches between the columns. Leave two line spaces
between the last author listed and the text of the paper. The left
margin should be 0.75 inches and the top margin should be 1 inch.
__The right and bottom margins will depend on whether you use
  U.S. letter or A4 paper, so you must be sure to measure the width of
  the printed text.__ Use 10~point Modern with 12~point vertical
spacing, unless otherwise specified.

The title should be in 14~point, bold, and centered. The title should
be formatted with initial caps (the first letter of content words
capitalized and the rest lower case). Each author's name should appear
on a separate line, 11~point bold, and centered, with the author's
email address in parentheses. Under each author's name list the
author's affiliation and postal address in ordinary 10~point type.

Indent the first line of each paragraph by 1/8~inch (except for the
first paragraph of a new section). Do not add extra vertical space
between paragraphs.

# First Level Headings

First level headings should be in 12~point, initial caps, bold and
centered. Leave one line space above the heading and 1/4~line space
below the heading.


## Second Level Headings

Second level headings should be 11point, initial caps, bold, and
flush left. Leave one line space above the heading and 1/4line
space below the heading.


### Third Level Headings

Third level headings should be 10point, initial caps, bold, and flush
left. Leave one line space above the heading, but no space after the
heading.


# Formalities, Footnotes, and Floats

Use standard APA citation format. Citations within the text should
include the author's last name and year. If the authors' names are
included in the sentence, place only the year in parentheses, as in
[-@NewellSimon1972a], but otherwise place the entire reference in
parentheses with the authors and year separated by a comma
[@NewellSimon1972a]. List multiple references alphabetically and
separate them by commas
[@ChalnickBillman1988a, @NewellSimon1972a]. Use the
``et~al.'' construction only after listing all the authors to a
publication in an earlier reference and for citations with four or
more authors.

`Rmarkdown` lets you generate figures in place. The default figure size can be set in the YAML front matter, but can also be set for each chunk of R code separately. To make sure they have enough space around them, use either `&nbsp` or LaTeX's `\newline`

&nbsp;

```{r plot test, echo=FALSE, fig.width=3.3, fig.height=3}
library(ggplot2)
mtcars$gear <- factor(mtcars$gear,levels=c(3,4,5),
  	labels=c("3gears","4gears","5gears"))
qplot(mpg, data=mtcars, geom="density", fill=gear, alpha=I(.5), 
   main="Distribution of Gas Milage", xlab="Miles Per Gallon", 
   ylab="Density")
```

&nbsp;


References are automatically placed at the end, but you need to provide a section header yourself:

# Bibliography
